### 2023-09-08 main.tex
fixed

\textbf{Proof of \eqref{k-times-QB}}

>>>>

\textbf{Proof of \eqref{k-times-QB}}: we can prove it inductively. For arbitrary $i\in\{1,\ldots,N-1\}$ it is true, since, using \eqref{ExQ0B-charges} and \eqref{Dij-ref} we have that 
	Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=&\left(B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,:\,\ell\neq i}^{N-1}B_{\ell}^{2L-1}D_{\ell,i}^{2L}\right)|\Psi_{0}^{0}\rangle\nonumber\\=&B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
We assume that it is true for all $k_{1},\ldots,k_{N-1}\in\{1,\ldots,N-1\}$ and we aim to show that, for all $i\in\{1,\ldots,N-1\}$,  
&\left(Q_{0}^{2L}B_{i}^{2L-1}\right)\prod_{\ell=1}^{N-1}\left(Q_{0}^{2L}B_{\ell}^{2L-1}\right)^{k_{\ell}}|\Psi_{0}^{0}\rangle=\left(B_{i}^{2L-1}\right)^{k_{i}+1}\prod_{\ell=1\,:\;\ell\neq i}^{N-1}\left(B_{\ell}^{2L-1}\right)^{k_{\ell}}\nonumber\\&\prod_{j=1}^{k_{1}+\ldots+k_{N-1}+1}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
it is also true. This can be shown by applying repeatedly \eqref{Two-Relation}.
